Meta-analysis

### 2020-02-17 05_MetaAnalysis.Rmd
Remove AUDPC analysis to add to separate file

## AUPDC and PM severity meta-analysis

```{r LM_AUDPC}
summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))

@@

Area under the disease progress curve (AUDPC) shows no linear relationship with the grain yield data when analysed without respect to any other factor. Lets use a mixed effect model which incorporates `trial` as a random effect. This makes sense given when we plotted the data subset by trial we could see a better relationship between grain yield and AUDPC.

```{r LMER_AUDPC1}
Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
              data = slimmer_PM_dat)
summary(Me_mod1)
```

AUDPC becomes a significant predictor of grain yield when the random effect `trial` is accounted for. However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial. Lets see if the model improves when AUDPC is used as a random slope for trial.

```{r LMER_AUDPC2}
Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
              data = slimmer_PM_dat)
anova(Me_mod1, Me_mod2)

```
The model is significantly improved, lower AIC and a higher log likelihood.

```{r LMER_AUDPC2_results}
summary(Me_mod2)
coef(Me_mod2)[["trial"]][
   order(coef(Me_mod2)[["trial"]]$AUDPC_m),]
```
Here the intercept represents an estimate of the trial yield without the limitation of the disease. AUDPC_m shows the slope of the regression for grain yield as AUDPC increases. The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope. In other words higher yielding mungbean crops were likely to see greater losses from disease.

Lets compare the area under the disease progress curve (AUDPC) to final severity.
```{r LMER_finalSev}

Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
              data = slimmer_PM_dat)
summary(Me_mod3)

Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
              data = slimmer_PM_dat)
summary(Me_mod4)

anova(Me_mod3, Me_mod4)

Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC.

We shall proceed by including the spray management predictor into the analysis.

```{r AUDPC_spraymanagement}
Me_mod5 <- lmer(grain_yield.t.ha ~ AUDPC_m + spray_management+ (AUDPC_m|trial),
              data = slimmer_PM_dat)

Me_mod6 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
              data = slimmer_PM_dat)
summary(Me_mod6)
anova(Me_mod2, Me_mod5)
anova(Me_mod5, Me_mod6)

Me_mod7 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
              data = slimmer_PM_dat)

>>>>

```{r Save_meta_data}
write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")

@@
